Analysis

### 2021-01-14 analysis.Rmd
small fix
initial commit

Ask Suzanne for raw data. Not sure how they rescaled the ordinal report data. Just a comment. I'd never tranform the factors into numbers scaled between 0-1. This leads to a loss of information.

@@

Correlation plots. Note that we need the to model the country level dependences in any correlation matrix, given strong cultural differences

>>>>

Ask Suzanne for raw data. Not sure how they rescaled the ordinal report data. Just a comment. I'd never trasnform the factors into numbers scaled between 0-1. This leads to a loss of information.

@@

Correlation plots. Note that we need the to model the country level dependencies in any correlation matrix, given strong cultural differences
